\documentclass{tccv}
\usepackage[english]{babel}

\begin{document}

\part{Matthew Martin}

\section{Work experience}

\begin{eventlist}

\item{July 2014 -- Present}
     {Forsmarsh Group}
     {Senior Software Engineer I}

Shipped major rewrite and improvement of a python app for NIST.

.NET stack backend Development for VA website, mostly WebAPI and WCF. 

Ground up work on a Knockout-Typescript UI. Coaching, Pair Programming \& Interviewing.

\item{August 2012 -- July 2014}
     {CACI}
     {JavaScript and C\# Software Developer III }

Participate in a very large team to fix performance on a .NET backend 
report generator. Also wrote a significant amount of JavaScript to 
upgrade a desktop application to a Single Page Application. Automated builds.

\item{May 2008 -- August 2012}
     {Procentrix}
     {Senior Consultant}

Maintenance development for a .NET line of business application at TSA on a 
very small team. Paid down technical debt and shipped 40 releases. Maintained and groomed product backlog.

\item{May 2005 -- May 2008}
     {Dynamics Research Corporation (Engility)}
     {Software Developer III}

DBA and developer for data centric applications, including maintenance of
ASP \& ASP.NET 2.0 web front ends, ETL and stored procedures. Included in person work
with subject matter experts.

\item{October 1998 -- May 2005}
     {Prince William County}
     {Systems Developer I}

MS-Access and VB6 development for the Finance Department. Custom
development and maintenance for bill printing, accounting reports and
batch processing. Frequent end user interaction to identify needs and problems.

\end{eventlist}

\personal
    [wakayos.com]
    {111 Lee Avenue Apt 103\newline Takoma Park, MD 20912}
    {(571) 247 - 6010}
    {matthewdeanmartin@gmail.com}

\section{Education}

\begin{yearlist}

\item[University of Akron,\newline
Akron, Ohio]{1988 -- 1992}
     {Master of Economics}

\item[University of Akron,\newline
Akron, Ohio]{1987 -- 1988}
     {BSBA Finance}


\end{yearlist}

\section{Public projects}

\begin{yearlist}

\item{2015}
     {tp parser(\href{https://github.com/matthewdeanmartin/tokipona.parser/}{github.com/matthewdeanmartin})}
     {Natural Language Parser}

\end{yearlist}

\section{Management Skills}

\begin{factlist}
\item{Coaching}{Demonstrated at FMG}
\item{Interviewing}{ Demonstrated at CACI, FMG, Procentrix }
\item{Scrum \& Kanban}{ Experience with "scrum for one"}
\end{factlist}

\section{Software skills}

\begin{factlist}

\item{Expert level}
     {C\#, .NET 4.5, ASP.NET, JavaScript, MS-SQL, Visual Studio, TSQL, Web-API, WCF, NUnit}

\item{Good level}
     {Python, MVC 2.0-5.0, TypeScript, SVN, TFS, Intellij, Entity Framework, WIF}

\item{Intermediate}
     {Lua, PHP, CSS, MySQL, msbuild, IIS}

\item{Basic level}
     {C++, Lua, Java, Eclipse, PL-SQL, Angular}

\item{Can Learn Fast}
     {Ruby}

\end{factlist}

\end{document}
